---
title: "Activity: Nuclear Reactors"
author: "YOUR NAME HERE"
output: 
  html_notebook: 
    fig_height: 7
---

```{r}
library(tidyverse)

```

## Scrape the Data

```{r}
#My code here.... 
library(rvest)

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

# Remove null columns
Japan <- tableList[[21]][1:9]
# Rename columns
Japan <-
  Japan %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         type = Type,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = `Beginbuilding`,
         operation = `Commercialoperation`, 
         closure = Closed)
# Remove the first row
Japan <- Japan[-1,]
Japan
```

## Your turn: In what ways is the table tidy? How is it not tidy? What's different about it from a tidy table?

Colums like plantname has names of plants separated by space, which is not tidy. Other than that, it looks tidy.

## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 
Japan %>%
  ggplot(aes(x = lubridate::dmy(construction), y = as.numeric(netMW), color=type)) + 
  labs(y = "ractorID", x = "operation") +
  geom_point() 

```

In general, the newer are the reactors, the more net generation capacity it has. When it comes to the type, BWR seems to outperform other types.

## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 
library(gdata)
# Remove null columns
China <- tableList[[10]][1:9]
# Rename columns
China <-
  China %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         type = Type,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = `Beginbuilding`,
         operation = `Commercialoperation`, 
         closure = Closed)
# Remove the first two rows
China <- China[-1,]
China <- China[-1,]
#full outer join
JapanChina <- combine(China, Japan)
JapanChina
```

After reading some post on stackoverflow, I have decided to use combine function from gdata library, because it automatically adds the source of data to the combined dataset.

## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here
toGraph <- Japan %>%
  group_by(name) %>%
  mutate(reactorID = paste(name, row_number()))
toGraph %>%
  mutate(status_change = !is.na(status)) %>%
  ggplot(aes(x = lubridate::dmy(construction), y = reactorID, color=type)) + 
  geom_segment(aes(x = lubridate::dmy(construction), xend=lubridate::dmy(operation), yend=reactorID)) +
  labs(y = "reactorID", x = "operation")  +
  geom_point()
```
